\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{amsmath}

\title{Raytracer Performance Optimization Report}
\author{Dawood Kingafg6 \\ University Name \\ Course Name}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This report documents the profiling, analysis, and optimization of the raytracer project based on the trayracer codebase. The goal was to improve performance through memory optimizations, multithreading, and static analysis.
\end{abstract}

\tableofcontents
\newpage

\section{Introduction}
Briefly describe the goal of the assignment:
- Render a single frame using a CPU-based raytracer.
- Measure and optimize performance.
- Implement multithreading.
- Document all improvements and results.

\section{Project Setup}
Explain:
- Initial project cloning.
- CMake and Ninja build system.
- Basic benchmark program structure.
- Compilation environment (Linux, GCC version, etc.)

\section{Benchmarking}
Describe how the benchmark was tested:
- Command-line parameters: resolution, rays per pixel, number of spheres.
- Initial performance results (time taken, MRays/s).

\section{Profiling and Analysis}
\subsection{Tools Used}
List the tools you used:
- \texttt{perf}
- \texttt{valgrind} (massif, cachegrind)
- (Any other profilers if used)

\subsection{Findings}
Show initial bottlenecks:
- High CPU usage points
- Memory bottlenecks
- Expensive function calls

\section{Optimizations}
For each optimization:
\begin{itemize}
    \item Explain what was optimized
    \item How it was optimized
    \item Before/After performance numbers
\end{itemize}

Example subsections:
\subsection{Memory Access Optimization}
\subsection{Math Function Optimization}
\subsection{Multithreading}

\section{Multithreading Implementation}
Describe:
- How rendering was parallelized.
- Number of threads.
- Synchronization methods (mutexes, locks, etc.)
- Final multithreaded performance results.

\section{Results}
\begin{itemize}
    \item Table comparing initial vs optimized performance
    \item Final MRays/s achieved
    \item Graphs or charts (optional)
\end{itemize}

\section{Conclusion}
Summarize:
- Overall performance gain
- Lessons learned
- Possible future improvements

\section{References}
List any online resources, articles, or books you used.

\end{document}
